---
title: "RStudio Instructor Training"
author: "Adithi R. Upadhya"
date: "22/02/2022"
output: html_document
---

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
# if tidyverse is not installed 
# install.packages("tidyverse")
# if already installed 
library(tidyverse)
```

### Look at the first table band_members

```{r message = FALSE, warning = FALSE}
?band_members
glimpse(band_members)
```
### Look at the second table band_instruments

```{r message = FALSE, warning = FALSE}
glimpse(band_instruments) 
```

### Using dplyr, join tables band_members and band_instruments so that the common observations in the both table remain

```{r message = FALSE, warning = FALSE}
band_instruments %>% 
  inner_join(., band_members, by = "name") 
```

### Using dplyr, join tables band_members and band_instruments so that the common observations in the both table remain, but this time, use the `by` parameter as a named character vector

```{r message = FALSE, warning = FALSE}
band_instruments %>% 
  inner_join(., band_members, by = c("name" = "name")) 
```

### Now, using `left_join`, join band_instruments and band_members such that all the variables in band_instruments are retained


```{r message = FALSE, warning = FALSE, eval = FALSE}
--------- %>% 
  left_join(., ---------, by = "name") 
```
